Verifying Spatial Properties of Stencil Computation

### 2016-11-15 paper.tex
Change the title to 'Specifying and Verifying the Spatial Properties of Stencil Computations'
Simplify induction variable definition

\title{Specifying and Verifying the Spatial Properties of Stencil Computations}
%\titlebanner{DRAFT -- Do not distribute}
\authorinfo{}{}{}
%\preprintfooter{DO NOT DISTRIBUTE}

@@

\begin{definition}[Base induction variable]
  An integer variable is a \emph{base induction variable} (or simply
\emph{induction variable} for brevity) if it is the
  control variable of a ``for'' loop (or equivalent, \eg{},
  \texttt{do} in Fortran for our implementation) incremented by $1$
  per iteration. A variable is interpreted as a base induction
variable only within the scope of the loop body. Induction varaibles
are ranged over by $i, j, k$ throughout.
%TODO: consider mentioning derived, non-based induction variables
% as we did before.
\end{definition}

>>>>

\title{Verifying Spatial Properties of Stencil Computation}
%\titlebanner{DRAFT -- Do not distribute}
\authorinfo{}{}{}
%\preprintfooter{DO NOT DISTRIBUTE}

@@

\begin{definition}[Induction variable]
  An integer variable is an \emph{induction variable} if it is the control
  variable of a \texttt{for} loop incremented by $1$ per iteration. A variable
  is interpreted as an induction variable only within the scope of the loop
  body. Induction varaibles range over $i, j, k$ throughout.
%TODO: consider mentioning derived, non-based induction variables
% as we did before.
\end{definition}
